### 2014-06-21 docs/paper/paper.tex
add integrator 1d figures

\includegraphics[width=6in]{integrator-1d.eps} % FIXME software plot
% FIXME figure: larger axis and label font, make this consistent across all figures

\caption[Simulation of a 1D neural integrator.]
{Hardware output from simulation of a one-dimensional population representing a neural integrator.}

>>>>

\begin{subfigure}[a]{0.4\textwidth}
\includegraphics[width=4in]{integrator-1d.eps}
\caption{Hardware simulation}
\label{fig:integrator1d:hw}
\end{subfigure}

\begin{subfigure}[b]{0.4\textwidth}
\includegraphics[width=4in]{integrator-1d-sw.eps}
\caption{Software simulation}
\label{fig:integrator1d:sw}
\end{subfigure}

% FIXME figure: larger axis and label font, make this consistent across all figures

\caption[Simulation of a 1D neural integrator.]
{Hardware (\ref{fig:integrator1d:hw}) and software (\ref{fig:integrator1d:sw}) output from simulation of a one-dimensional population representing a neural integrator.}
